Combining checkpointing and data compression\\ for high frequency seismic imaging

### 2018-10-03 paper/paper.tex
revised Introduction

In this paper, we extend the previous studies by \emph{combining} checkpointing
and compression. An obvious use case would be one where the data does not fit
in the available memory even after compression. This could happen either for
very large adjoint problems, or for problems where the required accuracy limits
the achievable compression ratios.

>>>>

In this paper, we extend the previous studies by \emph{combining} checkpointing
and compression. This is obviously useful when the data does not fit in the
available memory even after compression, for example for very large adjoint
problems, or for problems where the required accuracy limits the achievable
compression ratios.
